\section*{Thematic Guide to Appendices}

This guide outlines the purpose and logical status of each appendix. While the core manuscript is analytically complete and modularly self-contained, the appendices provide rigorous justifications, formal background, and speculative extensions. Each is labeled as one of:

\begin{center}
\textit{[A] Analytic Infrastructure} \quad
\textit{[E] Optional Enhancement} \quad
\textit{[S] Speculative Outlook}
\end{center}

\begin{description}
  \item[\textbf{\appref{app:notation_summary}}] \textbf{Summary of Notation [A]} \\
  Global definitions of analytic objects, operators, weight conventions, and spectral mappings used throughout.

  \item[\textbf{\appref{app:dependency_graph}}] \textbf{Logical Dependency Graph [A]} \\
  Directed acyclic structure of the proof system: chapter-by-chapter dependency DAG encoding lemma–theorem hierarchy.

  \item[\textbf{\appref{app:zeta_function_background}}] \textbf{Zeta Function Background [A]} \\
  Classical properties of \( \zeta(s) \), \( \Xi(s) \), and their Hadamard factorization and critical-line symmetries.

  \item[\textbf{\appref{app:trace_ideals_review}}] \textbf{Trace Ideals and Determinants [A]} \\
  Review of Schatten classes, trace-norm convergence, and Carleman \(\zeta\)-regularized Fredholm determinant theory.

  \item[\textbf{\appref{app:reductions_and_conventions}}] \textbf{Global Analytic Conventions [A]} \\
  Functional normalizations, domain and weight settings, and symmetry conventions for Fourier and kernel operators.

  \item[\textbf{\appref{app:heat_kernel_construction}}] \textbf{Heat Kernel Justifications [A]} \\
  Detailed derivations supporting trace-class convergence, Laplace integrability, and diagonal kernel asymptotics in Chapter~\ref{sec:heat_kernel_asymptotics}.

  \item[\textbf{\appref{app:heat_kernel_refinements}}] \textbf{Refinements (Noncritical) [E]} \\
  Subleading heat trace terms, arithmetic regularity conjectures, and potential improvements to Tauberian remainders.

  \item[\textbf{\appref{app:spectral_numerics}}] \textbf{Numerical Simulations (Heuristic) [E]} \\
  Discrete approximations to eigenvalues, convergence of \( L_t \to L_{\sym} \), and determinant growth numerics.

  \item[\textbf{\appref{app:functorial_extensions}}] \textbf{Functorial Extensions (Speculative) [S]} \\
  Proposed generalizations to automorphic \( L \)-functions, spectral Langlands duality, and categorical trace frameworks.

  \item[\textbf{\appref{app:additional_structures}}] \textbf{Further Directions [S]} \\
  Structural conjectures including motivic cohomology, determinant identities for motives, and universal zeta symmetries.

  \item[\textbf{\appref{app:spectral_physics_link}}] \textbf{Spectral Physics Perspective [S]} \\
  Heuristic interpretation of \( L_{\sym} \) as a quantum Hamiltonian; the heat trace as a regularized partition function.
\end{description}
