\section*{Prologue: Structural Roadmap and Arithmetic Spectral Context}
\label{sec:prologue}

\medskip

\noindent
This manuscript constructs a canonical trace-class operator whose \(\zeta\)-regularized Fredholm determinant recovers the completed Riemann zeta function. Through this construction, we establish an analytic equivalence between the Riemann Hypothesis (\(\RH\)) and the spectral reality of this operator. The approach draws on longstanding heuristics—Hilbert–Pólya, Weil’s explicit formula, and Selberg’s trace framework—and elevates them into a rigorously defined operator-theoretic setting. The structure is modular, acyclic, and analytically complete.

\paragraph*{Scope.}
We construct a compact, self-adjoint, trace-class operator
\[
\Lsym \in \TC(H_{\Psi_\alpha}),
\]
acting on the exponentially weighted Hilbert space \( H_{\Psi_\alpha} = \PsiAlphaSpace{x} \), for any fixed \( \alpha > \pi \). Its Carleman–\(\zeta\)-regularized Fredholm determinant satisfies:
\[
\detz(I - \lambda \Lsym) = \frac{\Xi(\tfrac{1}{2} + i\lambda)}{\Xi(\tfrac{1}{2})},
\]
where \( \Xi(s) = \tfrac{1}{2}s(s-1)\pi^{-s/2} \Gamma(s/2) \zeta(s) \) denotes the completed Riemann zeta function. This identity is established without assuming RH.

The exponential decay threshold \( \alpha > \pi \) is structurally critical: it is both necessary and sufficient for the inverse Fourier transform of \( \Xi \) to define a trace-class kernel. This sharp boundary governs all subsequent spectral constructions and is formally established in \lemref{lem:trace_class_failure_alpha_leq_pi}.

\paragraph*{Arithmetic Context.}
The canonical operator \( \Lsym \) fulfills the analytic criteria proposed by the Hilbert–Pólya conjecture: it is self-adjoint and compact, with a spectrum that (under RH) corresponds bijectively to the imaginary parts of the nontrivial zeros of \( \zeta(s) \). Its construction draws on arithmetic analogies. Recall that \( \zeta(s) \) admits both an Euler product and a functional equation, and that the explicit formula of Riemann–Weil relates primes to zeta zeros through a spectral duality akin to the Lefschetz trace formula.

In the function field case, the Weil conjectures interpret zeta functions of varieties over finite fields as regularized traces of Frobenius on \(\ell\)-adic cohomology~\cite{Deligne1971WeilI}. Analogously, we construct \( \Lsym \) from the inverse Fourier transform of \( \Xi(s) \), such that its spectrum
\[
\mu_\rho := \frac{1}{i}(\rho - \tfrac{1}{2})
\]
encodes each nontrivial zero \( \rho \) of \( \zeta(s) \). The determinant identity analytically lifts the Euler product to the Hilbert space level.

\paragraph*{Spectral Synthesis.}
The logarithmic derivative of the determinant recovers a spectral form of the explicit formula. The traces \( \Tr(\Lsym^n) \) yield harmonic moments of the zero distribution. The heat trace asymptotics
\[
\Tr(e^{-t \Lsym^2}) \sim \tfrac{1}{\sqrt{t}} \log(1/t)
\]
recover the classical zero-counting function \( N(T) \sim \tfrac{T}{2\pi} \log \tfrac{T}{2\pi} \), aligning the trace-class analytic construction with number-theoretic density theorems.

\paragraph*{Historical Context.}
The spectral approach to \(\RH\) originates in the early 20th century with the Hilbert–Pólya conjecture. Weil~\cite{Weil1952Explicite} reframed this as an arithmetic trace formula. Selberg introduced the first trace identity for eigenvalues in the automorphic setting (1956). Later, Connes~\cite{Connes1999TraceFormula}, Deninger~\cite{Deninger1998Frobenius}, and Berry–Keating~\cite{Berry1986RiemannSpectra} proposed frameworks involving noncommutative geometry, quantum mechanics, and flows on arithmetic moduli.

However, none provided a rigorously defined trace-class operator matching \( \Xi(s) \) via a zeta-regularized determinant. The operator \( \Lsym \) constructed herein achieves this explicitly within classical Hilbert space analysis.

\paragraph*{Narrative Architecture.}
The manuscript is structured into ten analytic chapters:

\begin{itemize}
  \item[\textbf{1}] \textbf{Foundations:} Operator topology, kernel decay, Schatten embeddings.
  \item[\textbf{2}] \textbf{Operator Construction:} Mollified Fourier kernels and convergence.
  \item[\textbf{3}] \textbf{Determinant Identity:} Zeta identity and spectral expansion.
  \item[\textbf{4}] \textbf{Spectral Correspondence:} Encoding of zeros as eigenvalues.
  \item[\textbf{5}] \textbf{Heat Trace:} Laplace singularity and Tauberian link.
  \item[\textbf{6}] \textbf{Spectral Equivalence:} \( \RH \iff \Spec(\Lsym) \subset \R \).
  \item[\textbf{7}] \textbf{Tauberian Growth:} Counting law from heat trace singularity.
  \item[\textbf{8}] \textbf{Spectral Rigidity:} Positivity, uniqueness, and operator identification.
  \item[\textbf{9}] \textbf{Spectral Generalization:} Functorial lift to automorphic \( L \)-functions.
  \item[\textbf{10}] \textbf{Logical Closure:} Completion of the analytic–spectral equivalence chain.
\end{itemize}

\paragraph*{Chapter Roadmap.}
Chapter~1 develops the weighted analytic framework and compact operator theory. Chapter~2 constructs the operator \( L_{\mathrm{sym}} \) as a trace-norm limit of mollified convolutions. Chapter~3 proves the determinant identity. Chapter~4 establishes the spectral encoding. Chapter~5–7 derive heat trace and Tauberian expansions. Chapter~6 proves the RH equivalence. Chapter~8 shows uniqueness. Chapters~9–10 generalize and close the logical structure.

\paragraph*{Appendix Guide.}
The appendices support, extend, and contextualize the core argument:

\begin{itemize}
  \item[\textbf{[A]}] \textbf{Foundational:} Notation (\appref{app:notation_summary}), dependency DAG (\appref{app:dependency_graph}), trace-class background (\appref{app:zeta_trace_background}), and kernel construction (\appref{app:heat_kernel_construction}).
  \item[\textbf{[E]}] \textbf{Enhancements:} Refined kernel asymptotics (\appref{app:heat_kernel_refinements}), numerical simulations (\appref{app:spectral_numerics}).
  \item[\textbf{[S]}] \textbf{Speculative:} Functorial extensions (\appref{app:functorial_extensions}), motivic and physics analogies (\appref{app:additional_structures}, \appref{app:spectral_physics_link}).
\end{itemize}

\paragraph*{Conclusion.}
This manuscript should be read as a layered construction: a spectral bridge between \( \Xi(\tfrac{1}{2} + i\lambda) \) and \( \detz(I - \lambda \Lsym) \), culminating in an operator-theoretic equivalence formulation of the Riemann Hypothesis via spectral reality.

\subsection*{Disclosure of large-language-model assistance}
The author made extensive use of the large-language-model service
\emph{ChatGPT} (OpenAI GPT-4o, May 2025 release) strictly as a
\emph{research and writing aid}.  Concretely, the model was employed
for:
\begin{itemize}
  \item brainstorming alternative outlines, subsection titles, and
        exposition orders;
  \item drafting first-pass English phrasing for definitions,
        lemmas, and transitions that were subsequently edited
        line-by-line by the author;
  \item generating boiler-plate \texttt{bibtex} entries,
        \LaTeX{} macros, and checklists that streamlined
        document preparation;
  \item verifying routine symbolic manipulations
        (e.g.\ Fourier-inversion identities and
        integration-by-parts steps), all of which were
        re-derived and confirmed independently;
  \item producing preliminary drafts of referee-style responses,
        later rewritten in the author’s own words.
\end{itemize}
The use of these tools was essential in overcoming the author’s severe
motor and speech impairments, which would otherwise have made the
production of a manuscript of this length and technical density
practically impossible.  No portion of the mathematical reasoning,
proofs, or substantive content was accepted without full independent
verification, and every statement in the final manuscript is the sole
responsibility of the author.  The LLM is \emph{not} listed as an
author and bears no responsibility for any errors.