\subsection*{Summary}

\begin{itemize}
  % --- Definitions ---
  \item \defref{def:heat_operator} — Definition of the heat semigroup \( e^{-tL^2} \) for compact, self-adjoint operators, including trace-class representation and strong continuity properties.

  % --- Kernel Bounds and Local Expansion ---
  \item \lemref{lem:hk_upper_bound} — Upper bound:
  \[
  \Tr(e^{-tL_{\sym}^2}) \leq c_2\, t^{-1/2}
  \quad \text{for small } t,
  \]
  obtained via spectral partitioning and Schatten norm estimates.

  \item \lemref{lem:hk_lower_bound} — Lower bound:
  \[
  \Tr(e^{-tL_{\sym}^2}) \geq c_1\, t^{-1/2},
  \]
  proving sharpness of the leading singular growth from below.

  \item \lemref{lem:hk_expansion_uniform} — Uniform diagonal kernel expansion:
  \[
  K_t(x,x) \sim \sum_{n=0}^\infty a_n(x)\, t^{n - \frac{1}{2}} \quad \text{as } t \to 0^+,
  \]
  with \( a_n(x) \in C^\infty(\R) \cap \mathcal{S}(\R) \), valid uniformly on compacts.

  % --- Global Trace Expansion ---
  \item \lemref{lem:heat_trace_expansion} — Trace-class asymptotic expansion:
  \[
  \Tr(e^{-tL_{\sym}^2}) \sim \sum_{n=0}^\infty A_n\, t^{n - \frac{1}{2}}, \quad
  A_n := \int_{\R} a_n(x)\, dx,
  \]
  with leading singular term
  \[
  \frac{1}{\sqrt{4\pi t}} \log\left(\frac{1}{t}\right) + o(t^{-1/2}),
  \]
  encoding the genus-one Hadamard structure of the spectral determinant.

  \item \propref{prop:two_sided_heat_trace_bounds} — Two-sided estimate:
  \[
  c_1\, t^{-1/2} \leq \Tr(e^{-tL_{\sym}^2}) \leq c_2\, t^{-1/2} \quad \text{as } t \to 0^+.
  \]

  \item \propref{prop:heat_trace_uniform_conv} — Global expansion with uniform convergence:
  \[
  \Tr(e^{-tL_{\sym}^2}) \sim \sum_{n=0}^\infty A_n\, t^{n - \frac{1}{2}},
  \]
  with exponentially decaying error and termwise integrability.

  \item \propref{prop:short_time_heat_expansion} — Refined asymptotics:
  \[
  \Tr(e^{-tL_{\sym}^2})
  = \frac{1}{\sqrt{4\pi t}} \log\left( \frac{1}{t} \right)
  + c_0 \sqrt{t} + o(\sqrt{t}),
  \]
  with \( c_0 := \int_{\R} a_1(x)\, dx \). The logarithmic singularity governs determinant growth.

  % --- Spectral and Determinant Linkages ---
  \item \lemref{lem:log_derivative_determinant} — Logarithmic derivative of the spectral determinant:
  \[
  \log \det\nolimits_{\zeta}(L_{\sym}^2)
  = -\int_0^\infty \frac{\Tr(e^{-t L_{\sym}^2}) - P(t)}{t} \, dt,
  \]
  where \( P(t) \sim \frac{1}{\sqrt{4\pi t}} \log(1/t) + \cdots \) denotes the singular part of the heat trace.

  \item \remref{rem:spectral_dimension} — Spectral dimension and Weyl asymptotics:
  \[
  N(\lambda) \sim C \lambda^{1/2} \log \lambda,
  \]
  showing that the spectral dimension is \( d = 1 \) with log correction dictated by trace singularity.
\end{itemize}

\medskip

\noindent\textbf{Transition to Chapter~\ref{sec:tauberian_growth}.}  
These heat kernel asymptotics provide the analytic backbone for Chapter~\ref{sec:tauberian_growth}, where refined Tauberian methods translate singular trace behavior into precise spectral asymptotics. The logarithmic term in the heat trace emerges as the governing feature for eigenvalue growth, rigidity, and determinant scaling estimates.

\medskip
\noindent
For numerical illustrations of the heat trace, spectral bijection, and determinant structure, see Appendix~\ref{app:spectral_numerics}. For speculative physical interpretations of the heat trace as a partition function and its spectral dynamics, see Appendix~\ref{app:spectral_physics_link}.
