\begin{proof}[Proof of Lemma~\ref{lem:trace_distribution_positivity}]
Let \( \{ \mu_n \} \subset \mathbb{R} \) denote the discrete spectrum of the compact, self-adjoint operator \( L_{\mathrm{sym}} \), with each eigenvalue repeated according to its finite multiplicity.

\paragraph{(i) Well-Definedness and Temperedness.}
For \( \phi \in \mathcal{S}(\mathbb{R}) \), the operator \( \phi(L_{\mathrm{sym}}) \) is defined via spectral functional calculus:
\[
\phi(L_{\mathrm{sym}}) = \sum_n \phi(\mu_n) P_n,
\]
where \( P_n \) denotes the orthogonal projection onto the eigenspace corresponding to \( \mu_n \), and each \( P_n \) is of finite rank.

Since \( L_{\mathrm{sym}} \in \mathcal{C}_1(H_{\Psi_\alpha}) \), its eigenvalues \( \mu_n \to 0 \) and satisfy \( \sum_n |\mu_n| < \infty \). The Schwartz decay of \( \phi \in \mathcal{S}(\mathbb{R}) \) ensures that for any \( N \in \mathbb{N} \), there exists \( C_N > 0 \) such that
\[
|\phi(\mu_n)| \le C_N (1 + |\mu_n|)^{-N}.
\]
Choosing \( N \) large enough yields
\[
\sum_n |\phi(\mu_n)| < \infty,
\]
so the spectral trace
\[
\operatorname{Tr}(\phi(L_{\mathrm{sym}})) := \sum_n \phi(\mu_n)
\]
is well-defined and finite. Furthermore, the map \( \phi \mapsto \operatorname{Tr}(\phi(L_{\mathrm{sym}})) \) is continuous on \( \mathcal{S}(\mathbb{R}) \), bounded by a finite collection of Schwartz seminorms. Thus, it defines a tempered distribution on \( \mathbb{R} \).

\paragraph{(ii) Positivity.}
If \( \phi \in \mathcal{S}(\mathbb{R}) \) satisfies \( \phi(\lambda) \ge 0 \) for all \( \lambda \in \mathbb{R} \), then
\[
\operatorname{Tr}(\phi(L_{\mathrm{sym}})) = \sum_n \phi(\mu_n) \ge 0,
\]
since each term in the sum is nonnegative.

This positivity reflects the nonnegativity of the heat kernel \( K_t(x, x) \) and its diagonal integral expansion. In particular, positivity is supported analytically by Proposition~\ref{prop:heat_trace_uniform_conv}, and the full decay and regularity justification in Appendix~\ref{app:heat_kernel_construction}.

\paragraph{Conclusion.}
The trace pairing \( \phi \mapsto \operatorname{Tr}(\phi(L_{\mathrm{sym}})) \) defines a positive tempered distribution on \( \mathbb{R} \), as claimed.
\end{proof}
