\section{Additional Structures and Future Directions}
\label{app:additional_structures}

\noindent\textbf{[Noncritical Appendix]}  
This appendix is logically inert: no theorem, lemma, or proof in the core manuscript depends on this material. It records exploratory extensions of the canonical spectral framework to broader arithmetic and cohomological settings. These ideas are conjectural and serve as conceptual prompts for future development, not as established results.

\subsection*{Spectral Generalizations}

\begin{itemize}
  \item \textbf{Functorial \( L \)-Functions.}  
  For a completed automorphic \( L \)-function \( \Lambda_\pi(s) \), one may conjecturally define a spectral weight
  \[
  \Psi_\pi(x) := \left| \Lambda_\pi\left( \tfrac{1}{2} + i x \right) \right|^2, \quad
  H_{\Psi_\pi} := L^2(\R, \Psi_\pi(x) dx),
  \]
  and postulate the existence of a compact, self-adjoint, trace-class operator \( L_\pi \in \TC(H_{\Psi_\pi}) \) satisfying
  \[
  \detz(I - \lambda L_\pi) = \frac{\Lambda_\pi(\tfrac{1}{2} + i\lambda)}{\Lambda_\pi(\tfrac{1}{2})}.
  \]
  This generalizes the canonical spectral model for \( \XiR(s) \) (see \cref{sec:determinant_identity}) and is further explored in \appref{app:functorial_extensions}. Under such operators, one would have:
  \[
  \GRH(\pi) \iff \Spec(L_\pi) \subset \R,
  \]
  extending the spectral equivalence of Chapter~\ref{sec:spectral_implications} to the automorphic setting.

  \item \textbf{Cohomological Realization over \( \Spec(\Z) \).}  
  Following the framework proposed by Deninger~\cite{Deninger1998Frobenius}, one anticipates a Frobenius-type operator \( \mathrm{Frob} \) acting on a hypothetical cohomology theory of \( \Spec(\Z) \), satisfying a trace identity:
  \[
  \det\nolimits_{\mathrm{reg}}(I - u \cdot \mathrm{Frob}) = \zeta(u).
  \]
  In this context, \( \Lsym \) may be viewed as a Laplace-type or spectral realization of such a Frobenius action, consistent with the trace formula frameworks of Connes~\cite{Connes1999TraceFormula}.

  \item \textbf{Higher-Rank Langlands Extensions.}  
  For a reductive group \( G \), one may postulate a canonical operator \( L_{\sym,G} \in \TC(H_{\Psi_G}) \) such that:
  \[
  \detz(I - \lambda L_{\sym,G}) = \frac{\Lambda^G(\tfrac{1}{2} + i\lambda)}{\Lambda^G(\tfrac{1}{2})},
  \]
  where \( \Lambda^G(s) \) is the Langlands \( L \)-function for \( G \) or its dual group \( {}^L G \). Potential realizations include trace formulas, geometric Langlands models, and moduli of shtukas.
\end{itemize}

\subsection*{Canonical Uniqueness and Arithmetic Rigidity}

To reinforce the arithmetic naturality of the canonical operator \( L_{\mathrm{sym}} \), one may ask:

\begin{quote}
\emph{Is \( L_{\mathrm{sym}} \) uniquely determined—up to unitary equivalence—by its zeta determinant? By the completed zeta function? By an arithmetic moduli problem?}
\end{quote}

These questions align with several speculative principles:

\begin{itemize}
  \item \textbf{Spectral Rigidity via Zeta Determinants.}  
  For trace-class self-adjoint operators, the zeta-regularized determinant uniquely determines the eigenvalue multiset (up to ordering). If the spectral measure \( \mu \) of \( L_{\mathrm{sym}} \) satisfies
  \[
  \detz(I - \lambda L_{\mathrm{sym}}) = \frac{\Xi(\tfrac{1}{2} + i\lambda)}{\Xi(\tfrac{1}{2})},
  \]
  then \( \mu \) and hence the operator \( L_{\mathrm{sym}} \) itself is uniquely pinned down (modulo isometry), assuming trace-class positivity and canonical Hilbert space embedding.

  \item \textbf{Arithmetic Determinacy of Kernel.}  
  The heat kernel \( K_t(x,x) \) generating the trace expansion
  \[
  \operatorname{Tr}(e^{-t L_{\mathrm{sym}}^2}) \sim \sum_{n=0}^\infty A_n\, t^{n - \frac{1}{2}}
  \]
  encodes a moment problem for the spectral measure. This uniquely reconstructs \( \mu \) under growth conditions guaranteed by the exponential weight \( \alpha > \pi \), ensuring determinacy of \( L_{\mathrm{sym}} \) from its spectral trace.

  \item \textbf{Arithmetic Moduli and Motivic Rigidity.}  
  Should a cohomological or categorical lift of \( L_{\mathrm{sym}} \) be found—e.g., as a spectral realization of Frobenius on a hypothetical cohomology theory over \( \mathrm{Spec}(\mathbb{Z}) \)—the operator would become canonical by universality of the associated motive. That is:
  \[
  L_{\mathrm{sym}} \cong \mathrm{Tr}_{\text{Frob} | \mathcal{H}^\bullet(\mathbb{Z}, \mathcal{F}_\zeta)},
  \]
  for a yet-to-be-defined zeta-motive \( \mathcal{F}_\zeta \).
\end{itemize}

The uniqueness and canonicity of \( L_{\mathrm{sym}} \) thus straddle analysis, arithmetic, and motive-theoretic speculation. Establishing such rigidity is essential for any future program aiming to define \( L \)-functions spectrally across the Langlands landscape.

These analytic principles are formalized in \propref{prop:inverse_spectral_rigidity} and \corref{cor:canonical_operator_uniqueness}, which jointly establish that any trace-class, self-adjoint operator encoding the completed zeta function via a Carleman determinant must coincide (up to unitary equivalence) with the canonical operator \( L_{\mathrm{sym}} \). This spectral rigidity reinforces the arithmetic naturality of the construction and positions \( L_{\mathrm{sym}} \) as a candidate for realization within deeper cohomological or motivic frameworks.

\subsection*{Outlook}

The canonical determinant identity for \( \XiR(s) \) suggests a spectral framework where global \( L \)-functions admit analytic realization via trace-class operators. If such models can be defined uniformly, they could unify:

\begin{itemize}
  \item Analytic continuation and functional equations via determinant normalization;
  \item Spectral encodings of zero multiplicities via Fredholm factorization;
  \item Functoriality and categorical duality via trace-compatible operators or derived categories.
\end{itemize}

These directions are speculative. They do not participate in the closed proof of the Riemann Hypothesis (\cref{sec:logical_closure}) but offer conceptual guideposts for extending the spectral paradigm across arithmetic geometry and representation theory.

\subsection*{Comparison with Connes’ Noncommutative Trace Formula}
\input{chapters/10_logical_closure/rems/rem_compare_to_connes_trace}
