\section{Spectral Physics Interpretation}
\label{app:spectral_physics_link}

\noindent\textbf{[Noncritical Appendix]}  
This appendix explores heuristic physical interpretations of the canonical operator \( L_{\sym} \in \TC(\HPsi) \). No physical model is constructed here. The analogy is strictly formal and logically inert. However, \( L_{\sym} \) admits a structure resembling a quantum Hamiltonian whose spectrum encodes the rescaled nontrivial zeros of the Riemann zeta function:
\[
\Spec(L_{\sym}) = \left\{ \mu_n := \frac{1}{\gamma_n} \;\middle|\; \zetaR\left(\tfrac{1}{2} + i\gamma_n\right) = 0 \right\}.
\]

\subsection*{Partition Function Analogy}

The heat trace
\[
Z(t) := \Tr(e^{-t L_{\sym}})
\]
resembles a partition function for a quantum system with energy levels \( \mu_n \). Its singular expansion:
\[
Z(t) \sim \frac{1}{\sqrt{4\pi t}} \log\left( \frac{1}{t} \right) + o(t^{-1/2}), \quad t \to 0^+,
\]
is typical of Laplace-type operators on singular spaces and reflects divergences observed in trace formulas on noncompact domains.

The zeta-regularized spectral determinant
\[
\log \det\nolimits_\zeta(I - \lambda L_{\sym})
\]
acts analogously to a regularized free energy in statistical mechanics. This reflects the spectral action principle in noncommutative geometry~\cite{Connes1999TraceFormula, Chamseddine2007SpectralAction}.

\subsection*{GUE Statistics and Inverse Spectrum}

Under the map
\[
\gamma_n \longmapsto \mu_n := \frac{1}{\gamma_n},
\]
the conjectured GUE distribution of zeta zeros~\cite{Montgomery1973PairCorrelation, Berry1986RiemannSpectra} transforms into a nonlinear spacing distribution on \( \Spec(L_{\sym}) \). This map compresses high-energy modes and magnifies low-frequency arithmetic structure.

Thus, \( L_{\sym} \) may be seen as a trace-class compression of an arithmetic Hamiltonian, capturing global zero statistics within an analytic framework.

\subsection*{Caveats and Interpretation}

These analogies do not influence any analytic result in the manuscript. No Hamiltonian, Lagrangian, or path integral is defined here.

Nonetheless, this viewpoint may motivate further inquiry into:
\begin{itemize}
  \item Quantum realizations of spectral zeta functions;
  \item Inverse-spectral statistics and trace-class ensembles;
  \item Hamiltonian interpretations of arithmetic trace formulas.
\end{itemize}

\medskip
\noindent
The operator \( L_{\sym} \) is a canonical analytic realization of the nontrivial zeta spectrum. Whether it admits a deeper physical interpretation—perhaps via quantization or arithmetic gauge theory—remains open.

\medskip
\noindent
For the analytic realization of the spectral equivalence \( \RH \iff \Spec(L_{\sym}) \subset \R \), see \cref{sec:spectral_implications}.
