\begin{definition}[Weighted Trace-Norm Space]\label{def:weighted-trace-norm-space}
Fix any \( \alpha > \pi \), and define the exponential weight
\[
\Psi_\alpha(x) := e^{\alpha |x|}, \qquad x \in \mathbb{R}.
\]
Let \( K \colon \mathbb{R}^2 \to \mathbb{C} \) be a measurable kernel. The \emph{weighted trace norm} is defined by
\[
\| K \|_{\mathcal{C}_1(\Psi_\alpha)} := \iint_{\mathbb{R}^2} |K(x,y)| \, \Psi_\alpha(x) \Psi_\alpha(y)\, dx\,dy.
\]
This defines the weighted trace-class kernel space
\[
\mathcal{C}_1(\Psi_\alpha) := \left\{ K \in L^1_{\mathrm{loc}}(\mathbb{R}^2) \ \middle|\ \| K \|_{\mathcal{C}_1(\Psi_\alpha)} < \infty \right\}.
\]

\medskip
\noindent\textbf{Trace-Class Realization.}
If \( K \in \mathcal{C}_1(\Psi_\alpha) \), then the integral operator
\[
(T_K f)(x) := \int_{\mathbb{R}} K(x,y)\, f(y)\, dy
\]
defines a bounded operator on the weighted Hilbert space \( H_{\Psi_\alpha} := L^2(\mathbb{R}, \Psi_\alpha(x)\, dx) \), and satisfies
\[
T_K \in \mathcal{C}_1(H_{\Psi_\alpha}).
\]

\medskip
\noindent\textbf{Trace-Norm Estimate.}
By Simon’s trace-class kernel criterion \cite[Thm.~4.2]{Simon2005TraceIdeals}, one has
\[
\|T_K\|_{\mathcal{C}_1(H_{\Psi_\alpha})} \le \|K\|_{\mathcal{C}_1(\Psi_\alpha)},
\]
so weighted kernel integrability controls trace-class membership in the Schatten \(\mathcal{C}_1\) ideal.

\medskip
\noindent\textbf{Convolution Kernel Case.}
Suppose \( K_t(x,y) = k_t(x - y) \) is a translation-invariant kernel with \( k_t \in L^1(\mathbb{R}, \Psi_\alpha^{-1}(x)\, dx) \). Then
\[
\| K_t \|_{\mathcal{C}_1(\Psi_\alpha)} = \left( \int_{\mathbb{R}} |k_t(z)| \Psi_\alpha(z)\, dz \right) \cdot \left( \int_{\mathbb{R}} \Psi_\alpha(x)\, dx \right) < \infty,
\]
so \( K_t \in \mathcal{C}_1(\Psi_\alpha) \), and the associated convolution operator
\[
L_t f(x) := \int_{\mathbb{R}} k_t(x - y)\, f(y)\, dy
\]
satisfies \( L_t \in \mathcal{C}_1(H_{\Psi_\alpha}) \) for all \( t > 0 \).

\medskip
\noindent\textbf{Spectral Role in Canonical Construction.}
The weighted kernel space \( \mathcal{C}_1(\Psi_\alpha) \) enables explicit and uniform trace-norm control of the mollified operator family \( \{L_t\}_{t > 0} \), with:
\[
L_t \xrightarrow{\ \mathcal{C}_1(H_{\Psi_\alpha})\ } L_{\mathrm{sym}} \in \mathcal{C}_1(H_{\Psi_\alpha}) \quad \text{as } t \to 0^+.
\]
This Schatten-class convergence ensures determinant convergence:
\[
\det\nolimits_\zeta(I - \lambda L_t) \to \det\nolimits_\zeta(I - \lambda L_{\mathrm{sym}})
\]
uniformly on compact subsets \( \lambda \in \mathbb{C} \). The weighted norm \( \|K\|_{\mathcal{C}_1(\Psi_\alpha)} \) thus offers a concrete test for trace-class inclusion, bypassing the need for diagonalization or kernel decomposition.

\medskip
\noindent\textbf{References.}
\begin{itemize}
    \item B. Simon, \emph{Trace Ideals and Their Applications}, Theorem~4.2 \cite{Simon2005TraceIdeals}.
\end{itemize}
\end{definition}
