\begin{definition}[Weighted Schwartz Space]\label{def:weighted_schwartz_space}
Let \( w \colon \mathbb{R} \to (0, \infty) \) be a smooth, strictly positive weight function satisfying:
\begin{enumerate}
    \item[\textup{(i)}] \( w(x) \ge 1 \) for all \( x \in \mathbb{R} \);
    \item[\textup{(ii)}] \( w(x) \to \infty \) as \( |x| \to \infty \);
    \item[\textup{(iii)}] \( w(x) \ge e^{\alpha |x|} \) for some \( \alpha > 0 \).
\end{enumerate}

The \emph{weighted Schwartz space} \( \mathcal{S}_w(\mathbb{R}) \) is the Fréchet space of all functions \( f \in C^\infty(\mathbb{R}) \) such that
\[
\| f \|^{(w)}_{k,\ell} := \sup_{x \in \mathbb{R}} \left| x^k f^{(\ell)}(x) \right| w(x)^{-1} < \infty \quad \text{for all } k,\ell \in \mathbb{N}_0.
\]
Each seminorm controls the weighted decay of derivatives; thus, functions in \( \mathcal{S}_w(\mathbb{R}) \) decay faster than any polynomial, modulated by exponential weight.

\medskip
\noindent\textbf{Topological Structure.}
\begin{itemize}
    \item There are continuous dense inclusions:
    \[
    \mathcal{S}(\mathbb{R}) \subset \mathcal{S}_w(\mathbb{R}) \subset L^2(\mathbb{R}, w(x)^{-2} dx).
    \]
    \item For exponential weights \( w(x) = e^{\alpha |x|} \), define \( \Psi_\alpha(x) := e^{2\alpha |x|} \), and the Hilbert space
    \[
    H_{\Psi_\alpha} := L^2(\mathbb{R}, \Psi_\alpha(x)\, dx).
    \]
    Then \( \mathcal{S}_w(\mathbb{R}) \subset H_{\Psi_\alpha} \), with dense embedding for all \( \alpha > 0 \).
\end{itemize}

\medskip
\noindent\textbf{Paley--Wiener Profile and Kernel Decay.}
Let \( \phi_t(\lambda) := e^{-t\lambda^2} \, \Xi\left( \tfrac{1}{2} + i\lambda \right) \) be the mollified spectral profile. Since \( \Xi(s) \) is entire of exponential type \( \pi \), the Paley--Wiener theorem yields:
\[
|k_t(x)| := \left| \mathcal{F}^{-1}[\phi_t](x) \right| \le C_\epsilon \, e^{-(\pi - \epsilon)|x|}, \quad \forall \epsilon > 0.
\]
Hence, for convolution kernels \( K_t(x,y) := k_t(x - y) \) and any \( \alpha > \pi \),
\[
K_t \in L^1(\mathbb{R}^2, e^{\alpha(|x| + |y|)} dx\,dy),
\]
and the associated operator
\[
L_t f(x) := \int_{\mathbb{R}} k_t(x - y)\, f(y)\, dy
\]
acts continuously on \( \mathcal{S}_w(\mathbb{R}) \) and preserves the space.

\medskip
\noindent\textbf{Spectral and Functional Role.}
The space \( \mathcal{S}_w(\mathbb{R}) \) serves as a common dense core for mollified convolution operators \( L_t \) and their trace-norm limit \( L_{\mathrm{sym}} \). Notable properties:
\begin{itemize}
    \item Stability under convolution: \( f \in \mathcal{S}_w \Rightarrow k_t * f \in \mathcal{S}_w \) for all \( t > 0 \);
    \item Density: \( \mathcal{S}_w(\mathbb{R}) \) is dense in \( H_{\Psi_\alpha} \) for all \( \alpha > 0 \);
    \item Trace class: if \( K_t \in L^1(\mathbb{R}^2, \Psi_\alpha(x)\Psi_\alpha(y)\, dx\,dy) \), then
    \[
    L_t \in \mathcal{C}_1(H_{\Psi_\alpha}) \quad \text{\cite[Thm.~4.2]{Simon2005TraceIdeals}}.
    \]
    \item Determinant continuity: the trace-norm convergence
    \[
    \det\nolimits_\zeta(I - \lambda L_t) \to \det\nolimits_\zeta(I - \lambda L_{\mathrm{sym}})
    \]
    holds uniformly on compact subsets \( \lambda \in \mathbb{C} \) as \( t \to 0^+ \), by norm continuity of the Fredholm determinant.
\end{itemize}

\medskip
\noindent\textbf{References.}
\begin{itemize}
    \item B.~Simon, \emph{Trace Ideals and Their Applications}, Theorem~4.2 \cite{Simon2005TraceIdeals}.
    \item B.~Ya.~Levin, \emph{Lectures on Entire Functions}, Chapter~9 \cite{Levin1996EntireLectures}.
\end{itemize}
\end{definition}
