\begin{proof}[Proof of Proposition~\ref{prop:strong_op_closure_heat}]
Let \( L := L_{\mathrm{sym}} \in \mathcal{C}_1(H_{\Psi_\alpha}) \) be the canonical compact, self-adjoint, nonnegative operator. By the spectral theorem, the heat semigroup \( \{ e^{-tL^2} \}_{t > 0} \) is defined via spectral functional calculus:
\[
e^{-tL^2} f = \sum_{n=1}^\infty e^{-t \mu_n^2} \langle f, e_n \rangle e_n,
\]
where \( \{e_n\} \subset H_{\Psi_\alpha} \) is an orthonormal basis of eigenfunctions with \( L e_n = \mu_n e_n \), and \( \mu_n \to 0 \).

\paragraph{Step 1: Strong Convergence.}
For any fixed \( f \in H_{\Psi_\alpha} \), we compute
\[
\| e^{-t L^2} f - f \|^2 = \sum_{n=1}^\infty \left( e^{-t \mu_n^2} - 1 \right)^2 |\langle f, e_n \rangle|^2.
\]
Since \( e^{-t \mu_n^2} \to 1 \) as \( t \to 0^+ \) for each \( n \), and \( \left| e^{-t \mu_n^2} - 1 \right| \le 2 \), the dominated convergence theorem implies:
\[
\lim_{t \to 0^+} \| e^{-t L^2} f - f \| = 0.
\]
Hence, \( e^{-tL^2} \to I \) strongly on \( H_{\Psi_\alpha} \) as \( t \to 0^+ \).

\paragraph{Step 2: Uniform Operator Bounds.}
For all \( t > 0 \), \( e^{-t L^2} \in \mathcal{B}(H_{\Psi_\alpha}) \cap \mathcal{C}_1(H_{\Psi_\alpha}) \), and satisfies
\[
\| e^{-t L^2} \|_{\mathcal{B}} \le 1,
\]
since \( L^2 \ge 0 \) implies contractivity of the semigroup. Moreover, the trace norm is finite:
\[
\| e^{-t L^2} \|_{\mathcal{C}_1} = \sum_{n=1}^\infty e^{-t \mu_n^2} < \infty,
\]
since the decay of \( \mu_n \to 0 \) ensures absolute summability of the heat weights for all \( t > 0 \).

\paragraph{Step 3: Analyticity and Equicontinuity.}
The semigroup \( \{ e^{-t L^2} \} \) is analytic in \( t \) and equicontinuous on norm-bounded subsets of \( H_{\Psi_\alpha} \), as it arises from a holomorphic semigroup generated by a positive compact self-adjoint operator.

\paragraph{Conclusion.}
Thus, \( \{ e^{-t L^2} \}_{t > 0} \subset \mathcal{C}_1(H_{\Psi_\alpha}) \) is a strongly continuous semigroup satisfying
\[
\lim_{t \to 0^+} e^{-t L^2} f = f, \qquad \forall f \in H_{\Psi_\alpha}.
\]
This completes the proof.
\end{proof}
