\begin{proof}[Proof of \lemref{lem:log_derivative_determinant}]
Let \( L := L_{\mathrm{sym}} \in \mathcal{C}_1(H_{\Psi_\alpha}) \) be the canonical compact, self-adjoint operator. The spectral zeta function is defined for \( \operatorname{Re}(s) > \tfrac{1}{2} \) by
\[
\zeta_L(s) := \sum_{\mu_n \neq 0} \mu_n^{-2s},
\]
where \( \{ \mu_n \} \subset \mathbb{R} \setminus \{0\} \) are the nonzero eigenvalues of \( L \), counted with multiplicity. By classical spectral theory and trace-class integrability, \( \zeta_L(s) \) extends meromorphically to \( \mathbb{C} \) with a regular point at \( s = 0 \); see~\cite[Ch.~3]{Simon2005TraceIdeals}.

\paragraph{Step 1: Zeta-Regularized Determinant.}
The logarithm of the zeta-regularized determinant is defined by
\[
\log \det\nolimits_\zeta(L^2) := -\left. \frac{d}{ds} \zeta_L(s) \right|_{s=0},
\]
provided \( \zeta_L(s) \) is analytic at \( s = 0 \). This regularity is ensured by subtracting off the singular part of the heat trace asymptotics via parametrix expansion.

\paragraph{Step 2: Mellin Representation and Heat Trace Subtraction.}
The zeta function admits the integral representation
\[
\zeta_L(s) = \frac{1}{\Gamma(s)} \int_0^\infty t^{s - 1} \operatorname{Tr}(e^{-t L^2}) \, dt,
\]
valid for \( \operatorname{Re}(s) > \tfrac{1}{2} \). However, the integrand diverges as \( t \to 0 \), due to the singular asymptotics of the heat trace. To define \( \zeta_L'(0) \), we subtract a parametrix \( P(t) \sim \sum_{n=0}^{N} A_n t^{n - \frac{1}{2}} \) such that \( \operatorname{Tr}(e^{-t L^2}) - P(t) \in L^1((0,\varepsilon)) \). Then:
\[
\log \det\nolimits_\zeta(L^2)
= -\int_0^\infty \frac{\operatorname{Tr}(e^{-t L^2}) - P(t)}{t} \, dt,
\]
which defines \( -\zeta_L'(0) \) via analytic continuation; see \appref{app:heat_kernel_construction} for full details.

\paragraph{Step 3: Logarithmic Singularity and Spectral Structure.}
From \propref{prop:short_time_heat_expansion}, the heat trace satisfies:
\[
\operatorname{Tr}(e^{-t L^2}) \sim \frac{1}{\sqrt{4\pi t}} \log\left( \frac{1}{t} \right) + c_0 \sqrt{t} + \cdots \quad \text{as } t \to 0^+.
\]
The leading term \( \frac{1}{\sqrt{4\pi t}} \log(1/t) \) is not integrable and must be subtracted to define the determinant. This term encodes the spectral dimension and the genus-one growth of the underlying zeta function.

\paragraph{Conclusion.}
The zeta-regularized determinant satisfies the trace-subtracted identity
\[
\log \det\nolimits_\zeta(L^2) = -\int_0^\infty \frac{\operatorname{Tr}(e^{-t L^2}) - P(t)}{t} \, dt,
\]
with
\[
P(t) \sim \frac{1}{\sqrt{4\pi t}} \log\left(\frac{1}{t}\right) + c_0 \sqrt{t} + \cdots,
\]
ensuring convergence and encoding the correct analytic and spectral behavior of \( \zeta_L(s) \) near the origin. This completes the proof.
\end{proof}
