\subsection*{Summary}

\begin{itemize}
  % --- Determinant Foundations ---
  \item Definition~\ref{def:fredholm-determinant} — Classical Fredholm determinant for trace-class operators, defined as a product over eigenvalues and analytic for all \( \lambda \in \mathbb{C} \).

  \item Definition~\ref{def:carleman-zeta-determinant} — Carleman \(\zeta\)-regularized determinant, defined via analytic continuation of a trace-exponential series for compact operators with trace-class powers.

  \item Definition~\ref{def:spectral-decomposition-compact} — Spectral decomposition for compact, self-adjoint operators: discrete spectrum with orthonormal eigenbasis and finite multiplicities.

  \item Definition~\ref{def:spectral-zeta-function} — Spectral zeta function \( \zeta_{L^2}(s) \), derived from eigenvalues and analytically continued via Mellin transform of the heat trace.

  % --- Convergence and Analytic Structure ---
  \item Lemma~\ref{lem:kernel-trace-norm-convergence} — Trace-norm convergence: mollified operators \( L_t \to L_{\mathrm{sym}} \) in \( \mathcal{C}_1 \), ensuring stability of analytic invariants.

  \item Lemma~\ref{lem:heat-trace-expansion} — Singular short-time heat trace expansion:
  \[
  \operatorname{Tr}(e^{-tL^2_{\mathrm{sym}}}) = \frac{1}{\sqrt{4\pi t}} \log\left(\frac{1}{t}\right) + \mathcal{O}(t^{-1/2}),
  \]
  characterizing the genus and exponential type of the determinant.

  \item Lemma~\ref{lem:det-via-heat-trace} — The determinant \( \log \det\nolimits_\zeta(I - \lambda L_{\mathrm{sym}}) \) is represented via the Laplace transform of the heat trace.

  \item Lemma~\ref{lem:laplace-heat-trace-convergence} — Laplace convergence of the heat trace ensures entire continuation of the determinant of order one and type \( \pi \).

  \item Lemma~\ref{lem:det_growth_bound} — Global growth bound: the determinant belongs to \( \mathcal{E}_1^{\leq \pi} \), the class of entire functions of order one and exponential type at most \( \pi \).

  \item Lemma~\ref{lem:det_identity_entire_order_one} — Sharp classification: the determinant exactly matches the Hadamard class of \( \Xi \), with order one and exponential type \( \pi \).

  % --- Hadamard and Spectral Matching ---
  \item Lemma~\ref{lem:exact-type-pi} — Exact exponential type \( \pi \) of both \( \Xi(\tfrac{1}{2} + i\lambda) \) and the canonical determinant.

  \item Lemma~\ref{lem:hadamard-linear-form} — Canonical Hadamard product structure matches spectral zeros of \( L_{\mathrm{sym}} \) to nontrivial zeros of \( \zeta(s) \).

  \item Lemma~\ref{lem:trace-zero} — Trace vanishing: \( \operatorname{Tr}(L_{\mathrm{sym}}) = 0 \) removes exponential ambiguity and normalizes \( \det\nolimits_\zeta(I) = 1 \).

  \item Lemma~\ref{lem:A_log_derivative} — Logarithmic derivative identity:
  \[
  \frac{d}{d\lambda} \log \det\nolimits_\zeta(I - \lambda L_{\mathrm{sym}})
  = \operatorname{Tr}\left( (I - \lambda L_{\mathrm{sym}})^{-1} L_{\mathrm{sym}} \right),
  \]
  valid on \( \mathbb{C} \setminus \operatorname{Spec}(L_{\mathrm{sym}}) \), confirming eigenvalue multiplicity and spectral encoding.

  % --- Canonical Identity Theorem ---
  \item Theorem~\ref{thm:det-identity-revised} — The canonical identity:
  \[
  \det\nolimits_\zeta(I - \lambda L_{\mathrm{sym}})
  = \frac{\Xi(\tfrac{1}{2} + i\lambda)}{\Xi(\tfrac{1}{2})},
  \]
  uniquely characterizes the determinant in \( \mathcal{E}_1^\pi \) by its zero set and normalization.

  % --- Tauberian and Spectral Asymptotics ---
  \item Lemma~\ref{lem:spectral_convexity_estimate} — From trace decay \( \operatorname{Tr}(e^{-tL^2}) \lesssim t^{-1/2} \), Tauberian theory yields
  \[
  N(\lambda) := \#\{ \mu_n^2 \le \lambda \} \lesssim \lambda^{1/2}.
  \]

  \item Proposition~\ref{prop:short_time_heat_expansion} — Refined trace expansion:
  \[
  \operatorname{Tr}(e^{-tL^2_{\mathrm{sym}}}) = \frac{1}{\sqrt{4\pi t}} \log(1/t) + c_0 \sqrt{t} + o(\sqrt{t}),
  \]
  determines the leading order growth of the determinant.

  \item Corollary (Chapter~\ref{sec:tauberian-growth}) — Spectral Tauberian inversion yields:
  \[
  N(\Lambda) \sim \frac{\sqrt{\Lambda}}{\pi} \log \Lambda,
  \]
  matching the Riemann–von Mangoldt formula for zero counting.
\end{itemize}

\medskip
\noindent
These results complete the analytic phase of the spectral program: the operator \( L_{\mathrm{sym}} \) canonically realizes the completed zeta function \( \Xi(s) \) via its \(\zeta\)-regularized Fredholm determinant. All analytic invariants—zero set, growth, and normalization—are uniquely determined. The spectral consequences of this identity are developed next in Chapter~\ref{sec:spectral-correspondence}.
% 