\begin{proof}[Proof of \thmref{thm:spectral_zero_bijection_revised}]
Let \( \rho = \tfrac{1}{2} + i\gamma \in \C \) be a nontrivial zero of the Riemann zeta function \( \zeta(s) \), and define its canonical spectral image:
\[
\mu_\rho := \frac{1}{i}(\rho - \tfrac{1}{2}) = \gamma.
\]

\paragraph{Injectivity.}
By \lemref{lem:zero_to_eigenvalue_injection}, the map \( \rho \mapsto \mu_\rho \in \Spec(\Lsym) \) is injective and multiplicity-preserving. Each nontrivial zero corresponds to a unique nonzero eigenvalue of \( \Lsym \), as guaranteed by the spectral theory of compact trace-class operators and the analytic structure of the Fredholm determinant.

\paragraph{Surjectivity.}
By \lemref{lem:spectral_exhaustivity}, every nonzero eigenvalue \( \mu \in \Spec(\Lsym) \setminus \{0\} \) arises from some nontrivial zero \( \rho \in \C \), via the inverse map \( \mu \mapsto \rho := \tfrac{1}{2} + i\mu \). The determinant \( \detz(I - \lambda \Lsym) \) admits no extraneous zeros.

\paragraph{Multiplicity Preservation.}
By \lemref{lem:spectral_multiplicity_matching}, the multiplicity of each eigenvalue \( \mu_\rho \in \Spec(\Lsym) \) matches the order of vanishing of \( \zeta(s) \) at \( \rho \). This is ensured by the Hadamard factorization of \( \Xi(s) \) and the spectral representation of the Fredholm determinant.

\paragraph{Conclusion.}
The spectral map
\[
\rho \longmapsto \mu_\rho := \tfrac{1}{i}(\rho - \tfrac{1}{2})
\]
defines a canonical, multiplicity-preserving bijection between the multiset of nontrivial zeros of \( \zeta(s) \) and the nonzero spectrum of \( \Lsym \in \TC(H_{\Psi_\alpha}) \). This correspondence is uniquely determined by the determinant identity and the spectral resolution of \( \Lsym \), and establishes a complete analytic encoding of the nontrivial zeta zeros.
\end{proof}
