\subsection*{Summary}

This chapter constructed the canonical convolution operator \( L_{\sym} \in \TC(H_{\Psi_\alpha}) \), beginning with mollified spectral profiles and culminating in a complete operator-theoretic classification. The results are modularly organized below:

\paragraph{Function Spaces and Core Definitions}
\begin{itemize}
  \item \defref{def:weighted_fourier_space} — Weighted Hilbert space \( H_{\Psi_\alpha} := L^2(\R, e^{\alpha |x|} dx) \) for \( \alpha > \pi \), enabling exponential kernel localization.
  \item \defref{def:canonical_fourier_profile} — Spectral profile \( \phi(\lambda) := \Xi(\tfrac{1}{2} + i\lambda) \), of exponential type \( \pi \), defining the zeta kernel.
  \item \defref{def:mollified_fourier_profile} — Mollifiers \( \varphi_t(\lambda) := e^{-t\lambda^2} \phi(\lambda) \in \Schwartz \) suppress high-frequency tails.
  \item \defref{def:convolution_operators_Lt_Lsym} — Definition of \( L_t \) via mollified convolution; canonical limit \( L_{\sym} := \lim_{t \to 0^+} L_t \in \TC(H_{\Psi_\alpha}) \).
\end{itemize}

\paragraph{Analytic Estimates and Kernel Decay}
\begin{itemize}
  \item \lemref{lem:mollified_profile_decay} — Uniform decay and Fourier integrability of mollified spectral kernels \( k_t(x) \).
  \item \lemref{lem:trace_class_Lt} — Simon’s criterion: \( L_t \in \TC(H_{\Psi_\alpha}) \) via weighted \( L^1 \) control.
  \item \lemref{lem:trace_norm_convergence_Lt_to_Lsym} — Strong convergence in \( \TC \): \( L_t \to L_{\sym} \).
  \item \lemref{lem:trace_norm_rate_convergence} — Quantified convergence rate: \( \|L_t - L_{\sym}\|_{\TC} \lesssim t^\beta \).
  \item \lemref{lem:trace_norm_limit_unique} — Trace-norm limit uniqueness: \( L_{\sym} \) is independent of mollifier sequence.
  \item \lemref{lem:construction_canonical_data} — Canonicality: \( L_{\sym} \) determined uniquely from \( (\Xi, \alpha) \).
  \item \lemref{lem:mollifier_independence_kernel_limit} — Kernel convergence is invariant under mollifier regularization.
\end{itemize}

\paragraph{Operator Properties and Domain Closure}
\begin{itemize}
  \item \lemref{lem:boundedness_Lsym} — Boundedness: \( L_{\sym} \in \mathcal{B}(H_{\Psi_\alpha}) \) from kernel bounds.
  \item \lemref{lem:core_essential_sa} — \( \Schwartz(\R) \subset H_{\Psi_\alpha} \) is a core for \( L_{\sym} \); essential self-adjointness follows.
  \item \lemref{lem:Lsym_square_selfadjoint} — Self-adjointness of \( L_{\sym}^2 \): positive operator with discrete spectrum.
  \item \remref{rem:selfadjoint_analytic_vectors} — Nelson's theorem ensures essential self-adjointness from mollifier structure.
  \item \lemref{lem:heat_semigroup_existence} — \( L_{\sym}^2 \) generates the analytic heat semigroup \( \{ e^{-t L_{\sym}^2} \}_{t > 0} \subset \TC(\HPsi) \).
\end{itemize}

\paragraph{Canonical Operator Theorems}
\begin{itemize}
  \item \thmref{thm:existence_Lsym} — Existence: \( L_{\sym} \in \TC(H_{\Psi_\alpha}) \) realized by mollified convergence.
  \item \thmref{thm:sa_trace_class_Lsym} — Final classification: \( L_{\sym} \) is compact, self-adjoint, and trace-class with exponentially decaying kernel.
  \item \thmref{thm:trace_zero_Lsym} — Trace vanishing: \( \Tr(L_{\sym}) = 0 \) enforces canonical normalization of the determinant.
\end{itemize}

\paragraph{Chapter Closure.}
This chapter delivers the full analytic realization of the canonical operator \( L_{\sym} \), with rigorously verified convergence, self-adjointness, trace-class regularity, and semigroup properties. Constructed explicitly from the mollified inverse Fourier transform of \( \Xi \), the operator \( L_{\sym} \) underlies the canonical determinant identity
\[
\det\nolimits_{\zeta}(I - \lambda^2 L_{\sym}^2) = \Xi\left(\tfrac{1}{2} + i\lambda\right),
\]
which is proved next in Chapter~\ref{sec:determinant_identity}.
