\subsection*{Introduction}

This chapter establishes the spectral asymptotics of the canonical compact, self-adjoint, trace-class operator
\[
L_{\mathrm{sym}} \in \mathcal{C}_1(H_{\Psi_\alpha}),
\]
via Laplace–Tauberian inversion of its squared heat semigroup. Using refined small-time asymptotics of the heat trace
\[
\Theta(t) := \operatorname{Tr}(e^{-t L_{\mathrm{sym}}^2}),
\]
we recover precise growth estimates for the eigenvalue counting function
\[
N(\Lambda) := \#\left\{ n \in \mathbb{N} : \mu_n^2 \le \Lambda \right\},
\]
and analytically verify compatibility with the Riemann–von Mangoldt zero-counting formula.

\paragraph{Objectives.}
\begin{itemize}
  \item \textit{Spectral Growth Bounds.}  
  From the heat trace envelope
  \[
  \Theta(t) \asymp t^{-1/2} \quad \text{as } t \to 0^+,
  \]
  established in Chapter~\ref{sec:heat-kernel-asymptotics}, we deduce via Lemma~\ref{lem:spectral_convexity_estimate} that
  \[
  N(\Lambda) = O(\Lambda^{1/2+\varepsilon}) \quad \text{for all } \varepsilon > 0,
  \]
  confirming subconvex spectral growth. The effective spectral dimension is \( d = 1 \), consistent with a leading law \( N(\Lambda) \sim \Lambda^{1/2} \log \Lambda \).

  \item \textit{Tauberian Inversion.}  
  Applying Korevaar’s refinement of Karamata theory (Lemmas~\ref{lem:tauberian-heat-trace-application},~\ref{lem:log-corrected-tauberian-application},~\ref{lem:tauberian-log-correction}), we invert the Laplace representation
  \[
  \Theta(t) = \int_0^\infty e^{-t\lambda} \, dN(\lambda),
  \]
  and obtain the precise growth law
  \[
  N(\Lambda) \sim \frac{1}{2\pi} \Lambda^{1/2} \log \Lambda \quad \text{as } \Lambda \to \infty.
  \]
  This follows from the classification \( \Theta \in \mathcal{R}_{1/2}^{\log} \), the space of regularly varying functions of index \( \frac{1}{2} \) modulated by a logarithmic factor.

  \item \textit{Zeta-Theoretic Compatibility.}  
  The derived growth law exactly matches the Riemann–von Mangoldt formula for the nontrivial zeros of the Riemann zeta function. This analytic agreement, established in Corollary~\ref{cor:zeta-compatibility}, provides direct confirmation that the spectrum of \( L_{\mathrm{sym}} \) encodes the zero distribution of \( \zeta(s) \).
\end{itemize}

\paragraph{Analytic Inputs from Chapter~\ref{sec:heat-kernel-asymptotics}.}

\begin{center}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{|c|X|X|}
\hline
\textbf{Source} & \textbf{Analytic Quantity} & \textbf{Role in This Chapter} \\
\hline
\textbf{Proposition~\ref{prop:two-sided-heat-trace-bounds}} &
\( \operatorname{Tr}(e^{-tL^2}) \asymp t^{-1/2} \) &
Ensures admissibility for Tauberian envelope bounds \\

\textbf{Proposition~\ref{prop:short_time_heat_expansion}} &
\( \operatorname{Tr}(e^{-tL^2}) = \frac{1}{\sqrt{4\pi t}} \log(1/t) + \cdots \) &
Triggers Korevaar inversion with logarithmic precision \\

\textbf{Lemma~\ref{lem:log-derivative-determinant}} &
Spectral zeta representation via heat trace &
Links eigenvalue asymptotics to determinant structure \\

\textbf{Remark~\ref{rem:spectral-dimension}} &
Spectral dimension \( d = 1 \), with \( N(\lambda) \sim \lambda^{1/2} \log \lambda \) &
Anchors growth law in RH-compatible zero distribution \\
\hline
\end{tabularx}
\end{center}
